---
title: "Stock Index Cointegration Analysis"
author: "Nova Nguyen"
date: "2023-10-17"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(astsa) 
require(xts)
require(dplyr)
library(tseries) # Augmented Dickey-Fuller test
require(lmtest) # Durbin Watson test
require(fBasics) # normality tests of residuals
require(leaps)
require(urca) # ERS test of stationarity
library(lubridate)
library(tidyr)
library(strucchange) 
library(aTSA)
library(vars)
library(tsDyn)
library(stargazer)
library(ggplot2)
```

## DATA PROCESSING

```{r Datasets}
#All cell information are read in as character variables

VNI <- read.csv("Datasets/VN Index Historical Data.csv")   # Vietnam
US <- read.csv("Datasets/SP500 Historical Prices.csv")   # US WSJ
CHN <- read.csv("Datasets/Shanghai Composite Historical Data.csv")   # China
HK <- read.csv("Datasets/Hang Seng Historical Data.csv")   # Hong Kong
JPN <- read.csv("Datasets/Nikkei 225 Historical Data.csv")   # Japan
SK <- read.csv("Datasets/KOSPI Historical Data.csv")   # South Korea
THL <- read.csv("Datasets/SET Index Historical Data.csv")   # Thailand
SGP <- read.csv("Datasets/STI Historical Prices.csv")   # Singapore WSJ
MSIA <- read.csv("Datasets/^KLSE.csv")   # Malaysia yahoo
PLP <- read.csv("Datasets/PSEi.PS.csv")   # Philippines yahoo
IND <- read.csv("Datasets/Jakarta Stock Exchange Composite Index Historical Data.csv")   # Indonesia
```

```{r Data Cleaning, warning = FALSE}

# Define a function for data processing
process <- function(data) {
  data = data %>%
    dplyr::select(Date, Price)
  data$Date = as.Date(data$Date, "%m/%d/%Y")  # Reformat and use Date type variable
  data$Price = as.numeric(gsub(",", "", data$Price))  # Remove comma string so R can read numeric
  data = data[order(data$Date),]  # Reorder the dataframe so time flows forward down the rows
  return(data)
}

# Apply the data processing function to each dataframe that can be generalized
VNI = process(VNI)
CHN = process(CHN)
HK = process(HK)
JPN = process(JPN)
SK = process(SK)
THL = process(THL)
IND = process(IND)

## US
US = US %>%
  dplyr:::select(Date, Close)
US$Date = as.Date(US$Date, "%m/%d/%y")
US = US[order(US$Date),]
US <- rename(US, Price = Close)

## SGP
SGP = SGP %>%
  dplyr:::select(Date, Close)
SGP$Date = as.Date(SGP$Date, "%m/%d/%y")
SGP = SGP[order(SGP$Date),]
SGP <- rename(SGP, Price = Close)

## MSIA
MSIA = MSIA %>%
  dplyr:::select(Date, Close)
MSIA$Date = as.Date(MSIA$Date)
MSIA = MSIA[order(MSIA$Date),]
MSIA <- rename(MSIA, Price = Close)
MSIA = MSIA %>%
  mutate(Price = round(as.numeric(Price), 2)) %>%
  drop_na()

## PLP
PLP = PLP %>%
  dplyr:::select(Date, Close)
PLP$Date = as.Date(PLP$Date)
PLP = PLP[order(PLP$Date),]
PLP <- rename(PLP, Price = Close)
PLP = PLP %>%
  mutate(Price = round(as.numeric(Price), 2)) %>%
  drop_na()

```


## SUMMARY STATISTICS

```{r Base index, warning = FALSE}
# List the dataframes  
dfs <- list(VNI, US, CHN, JPN, HK, SK, SGP, THL, MSIA, PLP, IND)

# Merge into one dataframe
df <- Reduce(function(x, y) merge(x, y, by = "Date", all = "True"), dfs)

# Rename columns
colnames(df) <- c("Date", "VNI", "US", "CHN", "JPN", "HK", "SK", "SGP", "THL", "MSIA", "PLP", "IND")

stargazer(df, type = "text")  
```

```{r % of daily return}

# Extracting the Date column
dates <- df$Date

# Calculating percentage returns for each index
returns_percent_df <- data.frame(Date = dates)  # Initialize a new dataframe with Date column

# Loop through columns (excluding Date) and calculate % returns
for (col in names(df)[-1]) {  # Exclude the first column (Date)
  returns_percent_df[[col]] <- c(NA, (df[[col]][-1] - df[[col]][-length(df[[col]])]) / df[[col]][-length(df[[col]])] * 100)
}

# Summarize the dataframe with % returns
stargazer(returns_percent_df, type = "text")

```

```{r}
# Correlation matrix of return %
round(cor(returns_percent_df%>%dplyr:::select(-Date), use = "na.or.complete"),4)
```



## TIME SERIES VISUALIZATION

```{r index price}
dfs <- list(VNI, US, CHN, JPN, HK, SK, SGP, THL, MSIA, PLP, IND)
dfnames <- list("VNI", "US", "CHN", "JPN", "HK", "SK", "SGP", "THL", "MSIA", "PLP", "IND")
par(mfrow = c(2,2))

for(i in 1:length(dfnames)){
  tsplot(dfs[[i]]$Date, dfs[[i]]$Price, main = dfnames[i], ylab = '', xlab = '')
}
```



```{r, warning = FALSE}
library(ggplot2)

dfs <- list(VNI, CHN, JPN, HK, SK)

dfnames <- c("VNI", "CHN", "JPN", "HK", "SK")
break_dates <- as.Date(c("2007-01-01", "2010-01-01", "2020-01-01", "2022-01-01"))

# Combine all data frames into a single data frame for ggplot
combined_df <- bind_rows(dfs, .id = "id") %>%
  mutate(id = as.factor(id))

# Plot using ggplot
ggplot(combined_df, aes(x = Date, y = log(Price), color = id)) +
  geom_line(size = 0.5) +
  geom_vline(xintercept = as.numeric(break_dates), color = "red") +
  scale_color_manual(values = c("#C61B1B", "#E1D81C", "#11690E", "#37E3D4", "#A44BD0"), labels = dfnames) +
  ylim(4.0, 11.0) +
  labs(x = '', y = "Logged Index Price", color = "Country") +
  theme_minimal() +
  theme(legend.position = "right")

```

```{r, warning = FALSE}

dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

dfnames <- c("VNI", "SGP", "THL", "MSIA", "PLP", "IND")
break_dates <- as.Date(c("2007-01-01", "2010-01-01", "2020-01-01", "2022-01-01"))

# Combine all data frames into a single data frame for ggplot
combined_df <- bind_rows(dfs, .id = "id") %>%
  mutate(id = as.factor(id))

# Plot using ggplot
ggplot(combined_df, aes(x = Date, y = log(Price), color = id)) +
  geom_line(size = 0.5) +
  geom_vline(xintercept = as.numeric(break_dates), color = "red") +
  scale_color_manual(values = c("#C61B1B", "#E1D81C", "#11690E", "#AD6F16", "#A44BD0", "#37E3D4"), labels = dfnames) +
  ylim(4.0, 11.0) +
  labs(x = "", y = "Logged Index Price", color = "Country") +
  theme_minimal() +
  theme(legend.position = "right")

```
```{r}
dfs <- list(VNI, US)

dfnames <- c("VNI", "US")
break_dates <- as.Date(c("2007-01-01", "2010-01-01", "2020-01-01", "2022-01-01"))

# Combine all data frames into a single data frame for ggplot
combined_df <- bind_rows(dfs, .id = "id") %>%
  mutate(id = as.factor(id))

# Plot using ggplot
ggplot(combined_df, aes(x = Date, y = log(Price), color = id)) +
  geom_line(size = 0.5) +
  geom_vline(xintercept = as.numeric(break_dates), color = "red") +
  scale_color_manual(values = c("#C61B1B", "#E1D81C"), labels = dfnames) +
  ylim(4.0, 11.0) +
  labs(x = "Date", y = "Logged Index Price", color = "Country") +
  theme_minimal() +
  theme(legend.position = "right")
```



## UNIT ROOT TEST

```{r}
dfs <- list(VNI, US, CHN, JPN, HK, SK, SGP, THL, MSIA, PLP, IND)
dfnames <- list("VNI", "US", "CHN", "JPN", "HK", "SK", "SGP", "THL", "MSIA", "PLP", "IND")
```


```{r stock index}

for(i in 1:length(dfs)){
  print(dfnames[i])
  print(tseries:::adf.test(log(as.data.frame(dfs[i])$Price)))
  print(tseries:::pp.test(log(as.data.frame(dfs[i])$Price)))
}
```

```{r stock return 1st difference, warning = FALSE}
for(i in 1:length(dfs)){
  print(dfnames[i])
  print(tseries:::adf.test(diff(log(as.data.frame(dfs[i])$Price))))
  print(tseries:::pp.test(diff(log(as.data.frame(dfs[i])$Price))))
}
```

## GRANGER CAUSALITY

Throughout this test, in testing for the number of VAR lags, we chose a good number as the max possible lags to be 10. We assume this would be sufficient to capture all short term price information as the Granger causality test is intended for determining short term linkages.

```{r VN - each country pre GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date < as.Date('2007-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```


```{r VN - each country during GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date >= as.Date('2007-01-01') & Date < as.Date('2010-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```


```{r VN - each country post GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date >= as.Date('2010-01-01') & Date < as.Date('2015-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```

```{r VN - each country pre Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date >= as.Date('2015-01-01') & Date < as.Date('2020-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```

```{r VN - each country during Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date >= as.Date('2020-01-01') & Date < as.Date('2023-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```

```{r VN - each country post Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  df <- df %>%
    filter(Date >= as.Date('2023-01-01')) %>%
    dplyr:::select(-Date)
  
  select <- VARselect(df, lag.max = 10)

  result1 <- grangertest(diff(log(df$VNI)), diff(log(df[,2])), order = as.numeric(select$selection[1]))
  result2 <- grangertest(diff(log(df[,2])), diff(log(df$VNI)), order = as.numeric(select$selection[1]))

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result1)
  print(result2)
}
```

##EG TEST

```{r EG pre GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2003-10-01"), Date < as.Date("2007-01-01"))

  result <- aTSA::coint.test(log(df$VNI), log(df[,3]), d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}

```


```{r EG during GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2007-01-01"), Date < as.Date("2010-01-01"))

  result <- aTSA::coint.test(log(df$VNI), log(df[,3]), d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}
```


```{r EG post GFC}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2010-01-01"), Date < as.Date("2015-01-01"))

  result <- aTSA::coint.test(log(df$VNI), log(df[,3]), d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}
```


```{r EG pre Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2015-01-01"), Date < as.Date("2020-01-01"))

  result <- aTSA::coint.test(df$VNI, df[,3], d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}
```


```{r EG during Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2020-01-01"), Date < as.Date("2023-01-01"))

  result <- aTSA::coint.test(df$VNI, df[,3], d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}
```


```{r EG post Covid}
for(i in 2:length(dfs)){

  # Merge VNI with each df
  df <- Reduce(function(x, y) merge(x, y, by = "Date"), list(VNI, dfs[i]))
 
  # Rename columns
  colnames(df) <- c("Date", "VNI", dfnames[i])
  
  df <- df %>%
  filter(Date >= as.Date("2023-01-01"))

  result <- aTSA::coint.test(df$VNI, df[,3], d = 0, output = TRUE)

  # Conduct ADF test on residuals
  print(dfnames[i])
  print(result)
}
```


##JOHANSEN COINTEGRATION TEST 

Throughout this test, in selecting VAR lag order, we assume that a good number for the max number of lags would be 7. 

```{r EA1, warning = FALSE}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #4
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 3, spec = "longrun")
summary(johansen)
```



```{r SEA1}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #7
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 6, spec = "longrun")
summary(johansen)
```


```{r EA2 pre GFC}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date < as.Date("2007-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #1
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```


```{r SEA pre GFC}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date < as.Date("2007-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #4
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```



```{r EA during GFC}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date >= as.Date("2007-01-01"), Date < as.Date("2010-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #2
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA during GFC}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2007-01-01"), Date < as.Date("2010-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #2
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA3 sans VNI during GFC}
dfs <- list(SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2007-01-01"), Date < as.Date("2010-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #2
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```



```{r EA post GFC}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date >= as.Date("2010-01-01"), Date < as.Date("2015-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #1
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA post GFC}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2010-01-01"), Date < as.Date("2015-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #4
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 3, spec = "longrun")
summary(johansen)
```



```{r EA pre Covid}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date >= as.Date("2015-01-01"), Date < as.Date("2020-01-01")) %>%
  dplyr:::select(-Date)

select <-VARselect(df, lag.max = 7, type = "const") #3
select$selection

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA pre Covid}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2015-01-01"), Date < as.Date("2020-01-01")) %>%
  dplyr:::select(-Date)

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```



```{r EA during Covid}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date >= as.Date("2020-01-01"), Date < as.Date("2023-01-01")) %>%
  dplyr:::select(-Date)

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA during Covid}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2020-01-01"), Date < as.Date("2023-01-01")) %>%
  dplyr:::select(-Date)

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```



```{r EA post Covid}
dfs <- list(VNI, CHN, JPN, HK, SK)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "CHN", "JPN", "HK", "SK")

df <- df %>%
  filter(Date >= as.Date("2023-01-01")) %>%
  dplyr:::select(-Date)

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```

```{r SEA post Covid}
dfs <- list(VNI, SGP, THL, MSIA, PLP, IND)

df <- Reduce(function(x, y) merge(x, y, by = "Date"), dfs)

colnames(df) <- c("Date", "VNI", "SGP", "THL", "MSIA", "PLP", "IND")

df <- df %>%
  filter(Date >= as.Date("2023-01-01")) %>%
  dplyr:::select(-Date)

johansen <- ca.jo(df, type = "eigen", ecdet = "none", K = 2, spec = "longrun")
summary(johansen)
```










